On exponential sums arising from the classical doubling method

### 2025-04-11 main.tex
Explaining why the proposition follows from the equalities

The results now follow from the equalities

@@

	\alpha(\zeta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots -q^{n-1}(y_{n}-y_{n+1}))})&= \alpha(\zeta^{(y_1+qy_{2n-1}+q^2y_3 +q^3y_{2n-3} \hdots +q^{n-1}y_{n+1})}) \\
	&\quad \cdot \alpha^{-1}(\zeta^{(qy_{2} + q^2y_{2n-2} + \hdots +q^{n-1}y_{n}+q^ny_{2n})}) \\
	\theta(\beta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\theta(\beta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})}) \\
	&=\theta'(\zeta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})})

@@

=
%Now the results follow from checking that
%\[
%    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
%\]
%for $r$ divisible as above.
\begin{comment}
Thus the result follows from the computations:
\begin{enumerate}
	\item[B,C,D Case 1] \begin{align*}
		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
		&= \alpha\left(\FieldNorm{mn}{n}(y_1(\zeta_{mn})\right) \alpha\left(\FieldNorm{mn}{n}(y_2(\zeta_{mn})\right)^{-1} \\
		&= \left(\alpha\times\alpha^{-1}\right)\left(\FieldNorm{mn}{n}((y_1,y_2)(\zeta_{mn}))\right)
	\end{align*}
	\item \begin{align*}
		\exp(\langle\phi(x_{\NormOneGroup{2n},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{2n},\theta},\phi^*(y_1,y_2)\rangle) \\
		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
		&= \theta'\left(\FieldNorm{2mn}{2n}((y_1,y_2)(\zeta_{mn}))\right)
	\end{align*}
\end{enumerate}
\end{comment}
\end{proof}

>>>>

Notice that we have the following equalities:

@@

The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition. This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that the coefficient of $q^i$ is $y_{i+1}$ for every $0 \le i \le 2n-1$.
%Now the results follow from checking that
%\[
%    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
%\]
%for $r$ divisible as above.
\begin{comment}
Thus the result follows from the computations:
	\item[B,C,D Case 1] \begin{align*}
		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
		&= \alpha\left(\FieldNorm{mn}{n}(y_1(\zeta_{mn})\right) \alpha\left(\FieldNorm{mn}{n}(y_2(\zeta_{mn})\right)^{-1} \\
		&= \left(\alpha\times\alpha^{-1}\right)\left(\FieldNorm{mn}{n}((y_1,y_2)(\zeta_{mn}))\right)

@@

		\exp(\langle\phi(x_{\NormOneGroup{2n},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{2n},\theta},\phi^*(y_1,y_2)\rangle) \\
		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
		&= \theta'\left(\FieldNorm{2mn}{2n}((y_1,y_2)(\zeta_{mn}))\right)
\end{proof}
